\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-14 paper/draft.tex
Opinions

\subsection{When to Use Dialysis}
\label{principles}
Dynamic analysis is a general analysis technique that discovering facts about programs.
While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
Dialysis can be thought as a coarser version of analysis stemming from the natural boundaries of libraries, a level of granularity that is just right for certain domains.
Which are these cases exactly?

The first class of  
It is really a quick-and-dirty 
As it quickly isolates homegrown code from standard libraries and third-party code, it is a help pin-point to 
Its availability as a global module makes this trivial.
% This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.

The second is when the goal is to understand the behavior of third-party code.
Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
Examples include the 
N-version programming ---all of which would require a custom tool.
By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.

Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
These limitations is due to several reasons.
First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
An important feature of the wrapping techniques presented in this paper is that they can ---\ie the full observable behavior around a library.
Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in its the program's address space.
A related problem is the inability to traverse and wrap objects, due to lack of bounds.
It is unclear how to wrap values without any kind of size information.\footnote{
  Recent efforts such as C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} show promise.
}
% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}

That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.

>>>>

\subsection{When to Use Dialysis}
\label{principles}
% Dynamic analysis is a general technique for discovering facts about programs.
While heavy-weight dynamic analysis provides full visibility into program execution, it may suffer from higher performance overheads, require significant developer effort, or offer results that are too low-level for the problem at hand.
% Dialysis can be thought as a coarser version of analysis stemming from natural library boundaries---a level of granularity that seems just right for certain problems.
% Which are these cases exactly?

% pressing need, lightweight, 
% multiplies lyas power
Dialysis shines when there is a need for urgency, select online analysis, and a high level of abstraction.
It can help identify (or narrow down) the source of a problem quickly, by swiftly isolating homegrown code from standard and third-party libraries, by requiring a few lines of analysis-specific code inlined, and by leveraging the developer's expertise in their language of choice.
By operating at coarser granularity, using the vanilla optimized runtime, and by toggling parts of the analysis on and off, it provides the ability to perform the analysis online.
Finally, dialysis deconstructs programs only at library boundaries, a naturally coarser granularity that is just the right level for certain problems.
% a granularity that is well-suited for several tasks.
% libraries are a convenient level of abstraction---or the point where abstractions 
% monitors all around a library

% The first class of problems where dialysis shines is quick-and-dirty insights;
% Even if dialysis doesn't solve the problem, it can quickly narrow it down to a certain corner of the application, at which point the cost of a heavy-weight solution is lower.
% % This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.
% 
% The second is when the goal is to understand the behavior of third-party code.
% Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
% Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
% Examples include the 
% N-version programming ---all of which would require a custom tool.
% By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.

Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
These limitations are due to several reasons.
First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
An important feature of the wrapping techniques presented in this paper is that they can track a library's full observable behavior.
Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in the program's address space.
A related problem is C's inability to traverse and wrap objects;
  due to lack of runtime information about size and structure, it is unclear how to traverse and transform them.\footnote{
  Recent efforts such as C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} show promise.
}
% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}

% That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
% Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
% Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
